\begin{thebibliography}{9}
\bibitem{1}
\href{https://ui.adsabs.harvard.edu/abs/2005Natur.435..629S/abstract}{V. Springel et al.},
\textbf{The Millennium Simulation}
\textit{Simulation of the formation, evolution and clustering of galaxies and quasars}
(Nature Publishing Group, 435-629, 2005).

\bibitem{2}
\href{https://ui.adsabs.harvard.edu/abs/2007MNRAS.375....2D/abstract}{G. De Lucia and J. Blaizot},
\textit{The hierarchical formation of the brightest cluster galaxies},
Monthly Notices of the Royal Astronomical Society, Volume 375, (2007).

\bibitem{3}
\href{https://ui.adsabs.harvard.edu/abs/2009MNRAS.398.1150B/abstract}{M. Boylan-Kolchin et al.} 
\textbf{The Millennium-II Simulation}
\textit{Resolving cosmic structure formation with the Millennium-II Simulation}
(MNRAS, 398-1150, 2009).

\bibitem{4}
\href{https://ui.adsabs.harvard.edu/abs/2013MNRAS.428.1351G/abstract}{Guo et al.} 
\textbf{The Millennium-WMAP7 Simulation}
\textit{Galaxy formation in WMAP1 and WMAP7 cosmologies}
(MNRAS, 428-1351, 2013).

\bibitem{5}
\href{https://ui.adsabs.harvard.edu/abs/2006astro.ph..8019L/abstract}{G. Lemson and the Virgo Consortium} 
\textbf{Datbase}
\textit{Halo and Galaxy Formation Histories from the Millennium Simulation: Public release of a VO-oriented and SQL-queryable database for studying the evolution of galaxies in the LambdaCDM cosmogony}
(2006)

\bibitem{6}
\href{http://gavo.mpa-garching.mpg.de/Millennium/}{Web: Virgo - Millennium Database}

\bibitem{7}
\href{https://ui.adsabs.harvard.edu/abs/2008MNRAS.383..546C/abstract}{Cole et al.} 
\textit{The statistical properties of $\Lambda$ cold dark matter halo information}
(Monthly Notices of the Royal Astronomical Society, 546-556, 2008).

\bibitem{8}
\href{https://ui.adsabs.harvard.edu/abs/2001MNRAS.328..726S/abstract}{Springel et al.} 
\textit{Population a cluster of galaxies - I. Results at [formmu2]z=0}
(Monthly Notices of the Royal Astronomical Society, 726-750, 2001).

\bibitem{9}
\href{https://github.com/Labalor/MillenniumSimulation/}{Código Python - Repositorio online}

\end{thebibliography}

